Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-30 prop_letter.tex
prop_letter.tex Introduction Updating...

The tension between finite precision measurement and the foundation
of quantum mechanics sharpened when the original definition of contextuality
based on infinitely precised numbers is proved not experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.
After a long debate~\cite{Mermin1999,Peres2003,BarrettKent2004},
people are still trying to update the definition of contextuality
when they want to perform further experiments~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

We found that finite precision measurement affects not only contextuality
but also the fundamental rule computing probability from a state.
In the early formulation of quantum mechanics, von Neumann essentially
formulated a quantum state as a density matrix while Mackey formulated
a quantum state as a probability measure which are proved to be the
same as a density matrix by Gleason's theorem~\cite{Varadarajan2008}.
If we follow Mackey's idea of probability measures together with the
classical IVPM~\cite{JamisonLodwick2004} which could be used to
formulate finite precision measurement in classical situation, we
can define quantum IVPMs. Surprisingly, there is a quantum IVPM which
can not be induced by a density matrix according to the Born rule.
Similar to the tension between finite precision and contextuality
are still inspiring experimental testable definition of contextuality,
the very basic definition of a quantum state or how to compute the
probability from a state might need to be refined when we consider
the finite precision measurement. \newpage{}

>>>>

The tension between finite precision measurement and the foundation
of quantum mechanics sharpened, when the original definition of contextuality
based on infinitely precised numbers is proved not experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.
After a long debate~\cite{Mermin1999,Peres2003,BarrettKent2004},
people are still trying to update the definition of contextuality
when they want to perform further experiments~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

We found that finite precision measurement affects not only contextuality
but also the fundamental rule computing probability from a state.
In the early formulation of quantum mechanics, von Neumann essentially
formulated a quantum state as a density matrix while Mackey formulated
a quantum state as a quantum probability measure which are proved
by Gleason to be the essentially same as a density matrix~\cite{Varadarajan2008}.
Combining quantum probability measures and the classical IVPM~\cite{JamisonLodwick2004}
which could be used to formulate classical finite precision measurement,
we can define quantum IVPMs. Surprisingly, there is a quantum IVPM
which cannot be compatible with any density matrix according to the
Born rule. Similar to revising the definition of contextuality because
of finite precision measurement, the very basic definition of a quantum
state or how to compute the probability from a state might need to
be refined when we consider the finite precision measurement. This
can also provides a new quantum phenomena different from the classical
world, because IVPMs become classical so that the non-Born IVPMs disappears
when we restricting the domain of quantum IVPMs on a commuting sub-event
space. \newpage{}
